The \dealii{} Library, Version 9.0

### 2018-04-23 9.0/paper.tex
Work through the incompatibilities section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{xxx something with Manifolds xxx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Use of C++11}
\dealii{} first offered support for a subset of C++11 features in
version 6.2, released in 2009. The current release is the first to
\emph{require} a C++11 compiler.

@@

\marginpar{OLD}
The 9.0 release includes around XYZ
\href{https://www.dealii.org/developer/doxygen/deal.II/changes_between_8_5_and_9_0.html}{
incompatible changes}; see \cite{changes90}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external applications. However, three
incompatible changes are worth mentioning:
\begin{itemize}
  \item High-order Lagrange elements, both continuous \verb!FE_Q! and
    discontinuous \verb!FE_DGQ! types, now use the nodal points of the
    Gauss-Lobatto quadrature formula as support points by default, rather than the
    previous equidistant ones. For cubic polynomials and higher, the point
    distribution has thus changed and, consequently, the entries in
    solution vectors will be different compared to previous
    versions of \dealii{}. Note, however, that using the Gauss-Lobatto points as nodal
    points results in a much more stable interpolation, including better
    iteration counts in most iterative solvers.
  \item
    The library no longer instantiates template classes with \texttt{long
    double}. These were rarely used, but took up a significant
    fraction of compile and link time, as well as library
    size. Application programs can, however, still instantiate all
    template classes with \texttt{long
    double} as long as they include the corresponding \texttt{.templates.h}
    header files.
  \item
    The \texttt{ParameterGUI} has been moved to a separate repository.
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{xxx something with Manifolds xxx}
\label{sec:manifolds}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \subsection{Use of C++11}
  \label{sec:cxx11}
\dealii{} first offered support for a subset of C++11 features in
version 6.2, released in 2009. The current release is the first to
\emph{require} a C++11 compiler.

@@

The 9.0 release includes
\href{https://www.dealii.org/developer/doxygen/deal.II/changes_between_8_5_and_9_0.html}
     {around 75 incompatible changes}; see \cite{changes90}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are, such as changes to the interplay between meshes and
manifolds, as well as the requirement to use a
C++11 compiler (see Sections~\ref{sec:manifolds} and
~\ref{sec:cxx11}). In addition, the following
incompatible changes are worth mentioning:
\begin{itemize}
\item The \texttt{BlockDiagonalMatrix},
  \texttt{InverseMatrixRichardson},
  \texttt{IterativeInverse},
  \texttt{ProductMatrix},
  \texttt{ProductSparseMatrix},
  \texttt{TransposeMatrix},
  \texttt{ScaledMatrix},
  \texttt{SchurMatrix},
  \texttt{ShiftedMatrix}, and
  \texttt{ShiftedMatrixGeneralized} classes have been removed. They are now
  generalized through the \texttt{LinearOperator} concept. Several
  other, similar classes have been deprecated.

  \item The default partitioner for the
    \texttt{parallel::shared::Triangulation} is now the Trilinos
    package Zoltan. This functionality was previously provided by the
    METIS partitioner, but the METIS package has not been actively maintained
    for a long time, and moreover yields subdivisions that depend on
    system details such as the random number generator and sorting
    facilities provided by the operating system; consequently, the
    partition is not consistent across platforms.

  \item  The class \texttt{FE\_DGQHermite}  now uses a more stable,
    ``Hermite-like'' polynomial basis. The change is highly
    beneficial because it significantly improves the accuracy (in
    terms of roundoff) for this basis and also reduces iteration
    counts for some iterative solvers with simple preconditioners.

  \item Many functions that previously returned a raw, C-style pointer
    now return a \texttt{std::unique\_ptr} and
    \texttt{std::shared\_ptr} where possible to make memory management
    more reliable.
\end{itemize}
